A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-13 manuscript.Rmd
add use_github()
fix list

@@

In software development, a release is the distribution of a piece of computer software indicating a certain maturity in development and level of completeness.
GitHub has a "release" function, which creates a link to a specific snapshot of your project that then is available as a single compressed file.
We believe that the idea of software releases can be leveraged for singling out important versions in a research project.
We found it useful to label the following stages of development as release:
- Preregistration (repository contains the final data analysis plan; also see the Section on PAC)
- Completion of data collection (repository contains all study data)
- Preprint (repository exactly reproduces a preprint that is hosted externally)
- Submission or Resubmission (repository exactly reproduces a given version (re)submitted to a journal)
- In Press (repository exactly reproduces the final manuscript as accepted by a scientific journal)

>>>>

```{r, eval=FALSE}
check_github()
```

@@

In software development, a release is the distribution of a piece of computer software indicating a certain maturity in development and level of completeness.
GitHub has a "release" function, which creates a link to a specific snapshot of your project that then is available as a single compressed file.
We believe that the idea of software releases can be leveraged for singling out important versions in a research project.
We found it useful to label the following stages of development as release:

* Preregistration (repository contains the final data analysis plan; also see the Section on PAC)
* Completion of data collection (repository contains all study data)
* Preprint (repository exactly reproduces a preprint that is hosted externally)
* Submission or Resubmission (repository exactly reproduces a given version (re)submitted to a journal)
* In Press (repository exactly reproduces the final manuscript as accepted by a scientific journal)
